Signal2Image Modules in Deep Neural Networks for EEG Classification

### 2025-10-16 packages/latex/ms.tex
init

@@

\begin{figure}[!t]
	\centering
	\begin{tikzpicture}[]
		\node[] at (-4.5, 0){\includegraphics[scale=0.2,angle=90]{python/tmp/signal-epilepsy.png}};
		\node[align=left] at (-4.2, 0) {$x_i$};
		\draw[dashed,->] (-4, 0) -- (-3.8, 0);
		\node[draw, minimum height=2.55cm] at (-3.5, 0) {$m$};
		\draw[dashed,->] (-3.2, 0) -- (-3, 0);
		\node[] at (-1.7, 0){\includegraphics[scale=0.41,angle=90]{python/tmp/cnn-epilepsy.png}};
		\draw[dashed,->] (-0.4, 0) -- (-0.2, 0);
		\node[draw, minimum height=2.55cm] at (0.1, 0) {$b_{d}$};
		\draw[dashed,->] (0.4, 0) -- (0.6, 0);
		\node[align=left] at (0.8, 0) {$\hat{y_i}$};
		\node[minimum width=0.5cm, minimum height=0.5cm] at (1.67, 1.1) {\footnotesize Open 0.1\%};
		\node[minimum width=0.5cm, minimum height=0.5cm] at (1.74, 0.55) {\footnotesize Closed 0.2\%};
		\node[minimum width=0.5cm, minimum height=0.5cm] at (1.78, 0) {\footnotesize Healthy 0.9\%};
		\node[minimum width=0.5cm, minimum height=0.5cm] at (1.8, -0.55) {\footnotesize Tumor 34.7\%};
		\node[minimum width=0.5cm, minimum height=0.5cm] at (1.9, -1.1) {\footnotesize Epilepsy 64.1\%};
	\end{tikzpicture}
	\caption{High level overview of a feed-forward pass of the combined methods.
	$x_i$ is the input, $m$ is the Signal2Image module, $b_{d}$ is the 1D or 2D architecture `base model' for $d=1,2$ respectively and $\hat{y_i}$ is the predicted output.
	The names of the classes are depicted at the right along with the predictions for this example signal.
	The image between $m$ and $b_{d}$ depicts the output of the one layer CNN Signal2Image module, while the `signal as image' and spectrogram have intermediate images as those depicted at the second and third row of Fig.~\ref{fig:signal2imageoutputs}.
	Arrows denote the flow of the feed-forward pass.
	For the 1D architectures $m$ is omitted and no intermediate image is generated.}\label{fig:highleveloverview}
\end{figure}

@@

\begin{figure*}[!t]
	\centering
	\rotatebox[origin=l]{90}{\small Original Signal}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.2]{python/tmp/signal-eyes-open.png}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.2]{python/tmp/signal-eyes-closed.png}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.2]{python/tmp/signal-healthy-area.png}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.2]{python/tmp/signal-tumor-area.png}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.2]{python/tmp/signal-epilepsy.png}
	\end{subfigure}

	\rotatebox[origin=l]{90}{\small `Signal as Image'}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{python/tmp/signal-as-image-eyes-open.png}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{python/tmp/signal-as-image-eyes-closed.png}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{python/tmp/signal-as-image-healthy-area.png}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{python/tmp/signal-as-image-tumor-area.png}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{python/tmp/signal-as-image-epilepsy.png}
	\end{subfigure}

	\rotatebox[origin=l]{90}{\small \hspace{1mm} Spectrogram}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{python/tmp/spectrogram-eyes-open.png}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{python/tmp/spectrogram-eyes-closed.png}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{python/tmp/spectrogram-healthy-area.png}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{python/tmp/spectrogram-tumor-area.png}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{python/tmp/spectrogram-epilepsy.png}
	\end{subfigure}

	\rotatebox[origin=l]{90}{\small \hspace{5mm} one layer CNN}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{python/tmp/cnn-eyes-open.png}
		\caption{Open}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{python/tmp/cnn-eyes-closed.png}
		\caption{Closed}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{python/tmp/cnn-healthy-area.png}
		\caption{Healthy}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{python/tmp/cnn-tumor-area.png}
		\caption{Tumor}
	\end{subfigure}
	\begin{subfigure}{0.19\linewidth}
		\centering
		\includegraphics[scale=0.5]{python/tmp/cnn-epilepsy.png}
		\caption{Epilepsy}
	\end{subfigure}
	\caption{Visualizations of the original signals and the outputs of the S2Is for each class.
	The x, y-axis of the first row are in \SI{}{\micro{} V} and time samples respectively.
	The x, y-axis of the rest of the subfigures denote spatial information, since we do not inform the `base model' the concept of time along the x-axis or the concept of frequency along the y-axis.
	Higher pixel intensity denotes higher amplitude.}\label{fig:signal2imageoutputs}
\end{figure*}

@@

\begin{table*}[!t]
	\caption{Test accuracies (\%) for combined models.
	The second row indicates the number of layers.
	Bold indicates the best accuracy for each base model.}\label{table:results}
	\begin{adjustbox}{width=\textwidth}
		\input{python/tmp/results.tex}
	\end{adjustbox}
\end{table*}

>>>>

\providecommand{\FILEPATH}{~/github.com/pbizopoulos/signal2image-modules-in-deep-neural-networks-for-eeg-classification/packages/python/tmp}

@@

\begin{figure}[!t]
  \centering
  \begin{tikzpicture}[]
    \node[] at (-4.5, 0){\includegraphics[scale=0.2,angle=90]{\FILEPATH/signal-epilepsy.png}};
    \node[align=left] at (-4.2, 0) {$x_i$};
    \draw[dashed,->] (-4, 0) -- (-3.8, 0);
    \node[draw, minimum height=2.55cm] at (-3.5, 0) {$m$};
    \draw[dashed,->] (-3.2, 0) -- (-3, 0);
    \node[] at (-1.7, 0){\includegraphics[scale=0.41,angle=90]{\FILEPATH/cnn-epilepsy.png}};
    \draw[dashed,->] (-0.4, 0) -- (-0.2, 0);
    \node[draw, minimum height=2.55cm] at (0.1, 0) {$b_{d}$};
    \draw[dashed,->] (0.4, 0) -- (0.6, 0);
    \node[align=left] at (0.8, 0) {$\hat{y_i}$};
    \node[minimum width=0.5cm, minimum height=0.5cm] at (1.67, 1.1) {\footnotesize Open 0.1\%};
    \node[minimum width=0.5cm, minimum height=0.5cm] at (1.74, 0.55) {\footnotesize Closed 0.2\%};
    \node[minimum width=0.5cm, minimum height=0.5cm] at (1.78, 0) {\footnotesize Healthy 0.9\%};
    \node[minimum width=0.5cm, minimum height=0.5cm] at (1.8, -0.55) {\footnotesize Tumor 34.7\%};
    \node[minimum width=0.5cm, minimum height=0.5cm] at (1.9, -1.1) {\footnotesize Epilepsy 64.1\%};
  \end{tikzpicture}
  \caption{High level overview of a feed-forward pass of the combined methods.
    $x_i$ is the input, $m$ is the Signal2Image module, $b_{d}$ is the 1D or 2D architecture `base model' for $d=1,2$ respectively and $\hat{y_i}$ is the predicted output.
    The names of the classes are depicted at the right along with the predictions for this example signal.
    The image between $m$ and $b_{d}$ depicts the output of the one layer CNN Signal2Image module, while the `signal as image' and spectrogram have intermediate images as those depicted at the second and third row of Fig.~\ref{fig:signal2imageoutputs}.
    Arrows denote the flow of the feed-forward pass.
  For the 1D architectures $m$ is omitted and no intermediate image is generated.}\label{fig:highleveloverview}
\end{figure}

@@

\begin{figure*}[!t]
  \centering
  \rotatebox[origin=l]{90}{\small Original Signal}
  \begin{subfigure}{0.19\linewidth}
    \centering
    \includegraphics[scale=0.2]{\FILEPATH/signal-eyes-open.png}
  \end{subfigure}
  \begin{subfigure}{0.19\linewidth}
    \centering
    \includegraphics[scale=0.2]{\FILEPATH/signal-eyes-closed.png}
  \end{subfigure}
  \begin{subfigure}{0.19\linewidth}
    \centering
    \includegraphics[scale=0.2]{\FILEPATH/signal-healthy-area.png}
  \end{subfigure}
  \begin{subfigure}{0.19\linewidth}
    \centering
    \includegraphics[scale=0.2]{\FILEPATH/signal-tumor-area.png}
  \end{subfigure}
  \begin{subfigure}{0.19\linewidth}
    \centering
    \includegraphics[scale=0.2]{\FILEPATH/signal-epilepsy.png}
  \end{subfigure}

  \rotatebox[origin=l]{90}{\small `Signal as Image'}
  \begin{subfigure}{0.19\linewidth}
    \centering
    \includegraphics[scale=0.5]{\FILEPATH/signal-as-image-eyes-open.png}
  \end{subfigure}
  \begin{subfigure}{0.19\linewidth}
    \centering
    \includegraphics[scale=0.5]{\FILEPATH/signal-as-image-eyes-closed.png}
  \end{subfigure}
  \begin{subfigure}{0.19\linewidth}
    \centering
    \includegraphics[scale=0.5]{\FILEPATH/signal-as-image-healthy-area.png}
  \end{subfigure}
  \begin{subfigure}{0.19\linewidth}
    \centering
    \includegraphics[scale=0.5]{\FILEPATH/signal-as-image-tumor-area.png}
  \end{subfigure}
  \begin{subfigure}{0.19\linewidth}
    \centering
    \includegraphics[scale=0.5]{\FILEPATH/signal-as-image-epilepsy.png}
  \end{subfigure}

  \rotatebox[origin=l]{90}{\small \hspace{1mm} Spectrogram}
  \begin{subfigure}{0.19\linewidth}
    \centering
    \includegraphics[scale=0.5]{\FILEPATH/spectrogram-eyes-open.png}
  \end{subfigure}
  \begin{subfigure}{0.19\linewidth}
    \centering
    \includegraphics[scale=0.5]{\FILEPATH/spectrogram-eyes-closed.png}
  \end{subfigure}
  \begin{subfigure}{0.19\linewidth}
    \centering
    \includegraphics[scale=0.5]{\FILEPATH/spectrogram-healthy-area.png}
  \end{subfigure}
  \begin{subfigure}{0.19\linewidth}
    \centering
    \includegraphics[scale=0.5]{\FILEPATH/spectrogram-tumor-area.png}
  \end{subfigure}
  \begin{subfigure}{0.19\linewidth}
    \centering
    \includegraphics[scale=0.5]{\FILEPATH/spectrogram-epilepsy.png}
  \end{subfigure}

  \rotatebox[origin=l]{90}{\small \hspace{5mm} one layer CNN}
  \begin{subfigure}{0.19\linewidth}
    \centering
    \includegraphics[scale=0.5]{\FILEPATH/cnn-eyes-open.png}
    \caption{Open}
  \end{subfigure}
  \begin{subfigure}{0.19\linewidth}
    \centering
    \includegraphics[scale=0.5]{\FILEPATH/cnn-eyes-closed.png}
    \caption{Closed}
  \end{subfigure}
  \begin{subfigure}{0.19\linewidth}
    \centering
    \includegraphics[scale=0.5]{\FILEPATH/cnn-healthy-area.png}
    \caption{Healthy}
  \end{subfigure}
  \begin{subfigure}{0.19\linewidth}
    \centering
    \includegraphics[scale=0.5]{\FILEPATH/cnn-tumor-area.png}
    \caption{Tumor}
  \end{subfigure}
  \begin{subfigure}{0.19\linewidth}
    \centering
    \includegraphics[scale=0.5]{\FILEPATH/cnn-epilepsy.png}
    \caption{Epilepsy}
  \end{subfigure}
  \caption{Visualizations of the original signals and the outputs of the S2Is for each class.
    The x, y-axis of the first row are in \SI{}{\micro{} V} and time samples respectively.
    The x, y-axis of the rest of the subfigures denote spatial information, since we do not inform the `base model' the concept of time along the x-axis or the concept of frequency along the y-axis.
  Higher pixel intensity denotes higher amplitude.}\label{fig:signal2imageoutputs}
\end{figure*}

@@

\begin{table*}[!t]
  \caption{Test accuracies (\%) for combined models.
    The second row indicates the number of layers.
  Bold indicates the best accuracy for each base model.}\label{table:results}
  \begin{adjustbox}{width=\textwidth}
    \input{\FILEPATH/results.tex}
  \end{adjustbox}
\end{table*}
